Location of Tuna farms

### 2021-03-15 marine/tuna/tuna_farms/STEP2_tuna_farm_locations.Rmd
checked over sources again

Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - If there are not exact numbers of farms in the country, but you know there are a lot, randomly place points along the coast line (a non-exact number, like we did for Taiwan). 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

@@

Source:
EMODnet Human Activities: Finfish production, 2019. [Accessed December 8, 2020] 
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production

>>>>

Now we will map the remaining countries with tuna farms that are not included in the ASC dataset. Workflow will be as follows: 
 - Try to obtain exact locations of farms from published source or dataset (such as FAO or a research paper)
 - If there are no exact locations, but the source lists a city or state, place a point in that particular city or state
 -  If there is enough information to know there are a specific number of shrimp farms, equally allocate the farms across the coastline. If there are estimates of farms per state/province, equally allocate them across the state/province, to be even more precise. 
 - Lastly, if there is no evidence of marine shrimp farm locations, place a point on the coast of the country (preferably with some intuition/knowledge of where they might be).

@@

Source:
EMODnet Human Activities: Marine Finfish Aquaculture, 2019. [Accessed December 8, 2020] 
https://www.emodnet-humanactivities.eu/search-results.php?dataname=Finfish+Production
